Jug: Software for Reproducible Computation

### 2011-12-08 paper.tex
TXT Add fan-in/fan-out. Discuss Hadoop

@@

>>>>

Figure~\ref{fig:jug-deps-complex} shows the dependency structure of this
examples. The main feature is the fan-out/fan-in which is associated with
map-reduce frameworks.

\begin{figure}
\begin{center}
\begin{tikzpicture}
\node (load) at (0,0) [draw] {load};
\node (collect) at (4,0) [draw] {collect};
\node (sum) at (8,0) [draw] {sum};
\node (output) at (10,0) [draw] {output};

\path[->]
    (sum) edge (output);

\foreach \y in {-2,-1,0,1,2} {%
    \node (features\y) at (2,\y) [draw] {features};
    \path[->]
        (load) edge (features\y)
        (features\y) edge (collect);
}

\foreach \y in {-2,-1,0,1,2} {%
    \node (fold\y) at (6,\y) [draw] {fold};
    \path[->]
        (collect) edge (fold\y)
        (fold\y) edge (sum);
}
\end{tikzpicture}

\end{center}
\caption{Dependency Structure for second example in the Text. The
fan-out/fan-in structure is typical (it is an instance of the map-reduce
framework).}
\label{fig:jug-deps-complex}
\end{figure}

@@

Jug was not designed to compete with more complex map/reduce frameworks such as
Hadoop, which scale better to very large projects. However, those frameworks
have much higher costs in terms of development time (code must be written
especially for the framework) and overhead (starting up and shutting down jobs
can take much longer and using non-Java code has additional computational
costs). For scientists using small to medium-sized cluster (hundreds, not
thousands, of nodes), with a shared file-system (as opposed to the distributed
file-systems necessary for truly large amounts of data) jug might provide a
better trade-off  than those higher-powered alternatives.
